Stochastic Wind Power Forecasting

### 2020-02-06 LaTeX_code/paper/paper_1line.tex
change figures in paper

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/data_1516064400.pdf}
  \includegraphics[width=60mm,scale=1]{plots/data_1516323600.pdf}\\
  \caption{Two samples from the Uruguayan of 2018. Each sample compromises of two 72-hour paths. In yellow is an hourly wind power production forecast. In blue is the actual wind power production recorded in 10 minute intervals. {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:sample_data}
\end{figure}

\begin{figure}
  \includegraphics[width=38mm,scale=1]{plots/hist_low.pdf}
  \includegraphics[width=38mm,scale=1]{plots/hist_mid.pdf}
  \includegraphics[width=38mm,scale=1]{plots/hist_high.pdf}
  \caption{We see that forecast errors exhibit skewness near the boundries (i.e. low and high power production regimes.). Low power is when produced power is less than $0.3$, mid power is when it is between $0.3$ and $0.6$ and high power when is larger than $0.6$.   {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:skew_data}
\end{figure}

\begin{figure}
  \includegraphics[width=38mm,scale=1]{plots/hist_low_lamperti.pdf}
  \includegraphics[width=38mm,scale=1]{plots/hist_mid_lamperti.pdf}
  \includegraphics[width=38mm,scale=1]{plots/hist_high_lamperti.pdf}
  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation. This motivates us to use a Gaussian transition density as a proxy density.  {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:skew_after_lamperti}
\end{figure}
%---END SECTION 1---

@@

\begin{equation}
 \arg\min \sum\limits_{i}^M \sum\limits_j^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 ,
 \end{equation}

@@

\begin{equation}
\theta_0 \alpha = \frac{1}{M} \sum\limits_i^M \frac{ \sum\limits_j^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_j^N x_{i,j}(1-x_{i,j}) } \,.
\end{equation}

>>>>

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Two samples from the Uruguayan of 2018. Each sample compromises of two 72-hour paths. In yellow is an hourly wind power production forecast. In blue is the actual wind power production recorded in 10 minute intervals. {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:sample_data}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_6.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_6.eps}
  \caption{We see that forecast errors exhibit skewness near the boundries (i.e. low and high power production regimes.). Low power is when produced power is less than $0.3$, mid power is when it is between $0.3$ and $0.6$ and high power when is larger than $0.6$.   {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:skew_data}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP.eps}
  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation. This motivates us to use a Gaussian transition density as a proxy density.  {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:skew_after_lamperti}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t.eps}
  \caption{Transitions.}
  \label{fig:skew_after_lamperti}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t_LP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t_LP.eps}
  \caption{Transitions after the Lamperti transform.}
  \label{fig:skew_after_lamperti}
\end{figure}
%---END SECTION 1---

@@

\begin{equation}
 \arg\min \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 ,
 \end{equation}

@@

\begin{equation}
\theta_0 \alpha = \frac{1}{M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
\end{equation}
